---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  fig.width = 9, 
  fig.height = 6
)
```

# nhmgrid: An R package for visualization of non-homogeneous Markov model probabilities

<!-- badges: start -->
[![Project Status: Inactive – The project has reached a stable, usable state but is no longer being actively developed; support/maintenance will be provided as time allows.](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
<!-- badges: end -->

The `nhmgrid` R package provides an easy-to-use interface for estimation and visualization of non-homogeneous Markov model transition probabilities. The main features in the package are:

* Supports a variety of model types in transition probability estimation using marginaleffects.
* Is able to calculate state transition proportions without a model.
* Produces highly customizable plots using ggplot2.

## Installation

You can install the most recent version of `nhmgrid` by running the following lines:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("joakim219/nhmgrid")
```

## Example

The package contains a simulated panel data set `health`. The data set consists
of 50 individuals whose health state has been measured every year for 10 years.

```{r}
library(nhmgrid)

head(health, 12)
nrow(health)
```

One can calculate the transition proportions between the health states using
`stprops` and plot them. Because the plot is constructed using ggplot2, it is
highly customizable.

```{r, props, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 4}
props <- stprops(health, x = "age", state = "state", id = "id")
plot(props) +
  ggplot2::geom_smooth(se = FALSE)
```

The transition probabilities between the states can be estimated with a Markov
model using `stprobs`. In this example we fit a multinomial logistic regression
model and estimate the probabilities separately for men and women.

```{r, probs, warning = FALSE, results = FALSE, fig.width = 9, fig.height = 4}
fit <- nnet::multinom(state ~ lagstate + age + sex, data = health)
probs <- stprobs(fit, x = "age", group = "sex")
plot(probs)
```

For more examples, see the package documentation.
